|

### 2020-02-05 nontex/install/git/fs_git_setup.Rmd
git setup incorporate conditional in bash

## Initalize and add remote repo for each:

@@

Pull latested from multiple repositories. Just Paste the following lines.

1. start ssh-agent secure session
2. pull from multiple Repositories upon start of working session.
3. commit changes as work on one computer
4. upon leaving a computer with commited changes, push all
5. create bash file to make it easier to repeat steps

@@

>>>>

## Initialize and add remote repo for each:

@@

Pull latest from multiple repositories. Just Paste the following lines.

1. start ssh-agent secure session
2. pull from multiple Repositories upon start of working session.
3. commit changes as work on one computer
4. upon leaving a computer with committed changes, push all
5. create bash file to make it easier to repeat steps

@@

# Conditional Pull, pull if some conditional satisfied
# For example, if a computer has some folder, pull to that.
if [ -d "D:/Dropbox (UH-ECON)/Project_Nguyen_Townsend_Wang_ThaiFinChoice/draft" ]
then
  echo "On Office Precision Desktop, Pull also for NTW Dropbox from Git Repo"
  cd "D:/Dropbox (UH-ECON)/Project_Nguyen_Townsend_Wang_ThaiFinChoice/draft"
  git pull github master
else
  echo "Not on office Precision, do not pull from NTW git repo to NTW Dropbox"
fi
